% !TeX spellcheck = en_GB
\chapter{Introduction}
The requirements document contains all mandatory requirements of the platform. They define the framework conditions and main goals we strive to achieve. Their core are functional and non-functional requirements, as well as a sketch of the overall system design. The draft takes into account the future environment and infrastructure in which the system will operate. 
\\\\
The details of the implementation will be published later by the programming team. In fact, the current requirements do not specify any technical solutions, in order to not restrict them while designing the technical aspects of the platform.
\\\\

Our requirements were created on the basis of the semester-requirements:\\

\begin{itemize}
\item Analysis of IT security in poor countries and crisis countries
\item Analysis of BSI IT security catalogs
\item develop and assign appropriate solutions
\item Construction of the platform:
\begin{itemize}
\item Dealing with increasing threats and threats / Change management / Updates
\item hardware used, software (commercial or open-source)
\item Web interface
\item Archive and search function
\item User roles
\item Design of the platform
\item Interfaces
\item Responsibilities and maintenance of data:
\begin{itemize}
\item Who is authorized or obliged to make changes to the database
make?
\item What precautions are necessary in terms of data protection?
\item Which information may be published in which form?
\end{itemize}
\end{itemize}
\item User guidance
\item Documentation of the project
\item Preparation of a workshop
\end{itemize}




